---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MRThreshold

<!-- badges: start -->
<!-- badges: end -->

The goal of MRThreshold is to simulate microrandomized trials subject to a capacity constrain.

## Installation

You can install the development version of MRThreshold from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("vsritter/MRThreshold")
```

## Example

To simulate the trajectory of 100 patients subject to a capacity of 5 (see the example of a model specification for the [*4T Sustainability Microrandomized Trial*](https://vsritter.github.io/MRThreshold/articles/microrandomization_setup.html))

```{r example}
library(MRThreshold)

RNGkind("L'Ecuyer-CMRG")
set.seed(365342)

sim_list <- sim_microrand(N = 100, capacity = 5)
sim_list
```

Then, users can compute the relevant metrics when designing their study, *e.g.*, bias, empirical standard error, coverage probability, and power.

```{r, include=FALSE}
library(tidyverse)
```


```{r}
# compute metrics
dt_res <- sim_list$lmer_reg %>% 
  group_by(sample_size, set, up_to_time) %>% 
  mutate(bias = estimate - b3,
         mse = bias^2,
         empirical_stderr = estimate - mean(estimate, na.rm = T),
         prop_rej = as.numeric(p.value < 0.05),
         ll = estimate - 1.96*std.error,
         ul = estimate + 1.96*std.error,
         cover = as.numeric((ll <= b3)*(b3 <= ul))) %>% 
  summarise(across(c(n_obs, n_clust, bias, empirical_stderr, mse, cover, prop_rej),
                   ~ mean(., na.rm = T)), .groups = 'drop')

dt_res
```

